Supplement: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
improved caption
edits re. hyperparameters

We define a prior distribution over DSLs which penalizes the sizes of the $\lambda$-calculus expressions in the DSL, and put a Dirichlet prior over the weight vector:
\begin{align*}
  \probability[\mathcal{D}]&\propto\exp\left(-\lambda\sum_{p\in \mathcal{D}}\text{size}(p) \right)\\
  \probability[\theta|\mathcal{D}]& = \text{Dir}(\theta|\alpha)
\end{align*}
where $\text{size}(p)$  measures the size of the syntax tree of program $p$,
$\lambda$ is a hyperparameter that acts as a regularizer on the size of the DSL,
and $\alpha$ is a concentration parameter controlling the smoothness of the prior over $\theta$.
%Alg.~\ref{grammarInductionAlgorithm} specifies the DSL induction algorithm.

@@

  \\\midrule\multicolumn{6}{c}{\emph{List functions (rich DSL)}}\\\midrule
  \% solved&\textbf{86\%} &84\% &60\%&74\%&70\%\\
  Solve time&  0.8s&0.7s&1.0s&1.0s&1.1s
  \\\bottomrule
  \end{tabular}
\caption{\% solved w/ 5 sec timeout. Solve time: averaged over solved tasks.
  RF/DC: trained like RobustFill/DeepCoder.
  PCFG: model w/o structure learning.
  Enum: model w/o learning.
  MDL: $-\expect\left[\probability[x|p] \right]$. For domains other than symbolic regression MDL is 0 nats. For symbolic regression MDL is a proxy for \# of continuous degrees of freedom.}\label{baselineComparisons}  \end{table}

>>>>

We define a prior distribution over DSLs which penalizes the sizes of the $\lambda$-calculus expressions in the DSL, and put a Dirichlet prior over the weight vector:
\begin{align}
  \probability[\mathcal{D}]&\propto\exp\left(-\lambda\sum_{p\in \mathcal{D}}\text{size}(p) \right)\\
  \probability[\theta|\mathcal{D}]& = \text{Dir}(\theta|\alpha)
\end{align}
where $\text{size}(p)$  measures the size of the syntax tree of program $p$,
$\lambda$ is a hyperparameter that acts as a regularizer on the size of the DSL,
and $\alpha$ is a concentration parameter controlling the smoothness of the prior over $\theta$.
%Alg.~\ref{grammarInductionAlgorithm} specifies the DSL induction algorithm.

@@

  \\\midrule\multicolumn{6}{c}{\emph{List functions (rich DSL)}}\\\midrule
  \% solved&\textbf{86\%} &84\% &60\%&74\%&70\%\\
  Solve time&  0.8s&0.7s&1.0s&1.0s&1.1s
  \\\bottomrule
  \end{tabular}
\caption{\% solved w/ 5 sec timeout. Solve time: averaged over solved
  tasks.  RF/DC: trained like RobustFill/DeepCoder.  PCFG: model w/o
  structure learning.  Enum: model w/o any learning.  MDL:
  $-\expect\left[\probability[x|p] \right]$. For domains other than
  symbolic regression MDL is 0 nats. For symbolic regression MDL is a
  proxy for \# of continuous parameters.}\label{baselineComparisons} \end{table}

### 2018-02-09 supplement.tex
edits re. hyperparameters

\section{Hyperparameters \& Implementation details}
We set $\alpha = 10$ and $\lambda = 1$ for all experiments except for string
editing. For string editing we found that more strongly regularizing
the DSL was necessary,
and so we set $\lambda = 5$.
We believe this is because
we have many more tasks for string editing than we do for the other domains.
The frontier size used for Boolean circuits was $5000$,
for symbolic regression we used $500$,
for string editing we used $10^5$,
and for list functions we used $10^4$.

>>>>

\section{Hyperparameters \& Implementation details}
We set structure penalty $\lambda = 1$ (Eq.~5 of the main paper) and
smoothness parameter $\alpha = 10$ (Eq.~6 of the main paper)
for all experiments except for string editing.
For string editing we found that more strongly regularizing
the DSL was necessary,
so we set $\lambda = 5$.
We believe this is because
we have many more tasks for string editing than we do for the other domains.
The frontier size used for Boolean circuits was $5000$,
for symbolic regression we used $500$,
for string editing we used $10^5$,
and for list functions we used $10^4$.
